Accelerated evolution of convective simulations

### 2018-02-27 tex/bvp_paper.tex
modified fig 4/ restructured [but did not edit, yet!] conclusions section

\section{Experiment}
\label{sec:experiment}
We study incompressible \RB convection under the Oberbeck-Boussinesq approximation,
such that our fluid
has a constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
of thermal expansion ($\alpha$). The density of the fluid is a constant, $\rho_0$,
except where it is $\rho = \rho_0(1  - \alpha T_1)$ on the term where
the constant gravitational acceleration, $\bm{g} = - g\hat{z}$, 
acts in the vertical momentum equation.
The equations of motion are \cite{spiegel&veronis1960}
\begin{gather}
\DivU = 0, 
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
-\frac{1}{\rho_0}\grad P - g( 1 - \alpha T_1)\hat{z} + \nu\grad^2\bm{u}, 
	\label{eqn:dim_bouss_momentum}
\\
\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \kappa\grad^2 T_1,
	\label{eqn:dim_bouss_energy}
\end{gather}
where $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$ is the velocity, 
$T = T_0 + T_1$ are the initial and fluctuating components of temperature, 
and $P$ is the pressure.
We non-dimensionalize these equations such that the
length is in units of the layer height ($L_z$),
temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
and velocity is in units of the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$).
by these choices, one time unit is a freefall time ($L_z/v_{\text{ff}}$).
We introduce a reduced kinematic pressure,
$\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where the gravitational
potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$. As $P$ is a
Langrange multiplier under the Oberbeck-Boussinesq approximation, $\varpi$
can be treated straightforwardly as a linear variable. 
In non-dimensional form, Eqns. \ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
become
\begin{gather}
\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} = \bm{u}\times\bm{\omega},
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1,
	\label{eqn:bouss_energy}
\end{gather}
where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
The dimensionless control parameters $\mathcal{P}$ and $\mathcal{R}$ 
are set by the Rayleigh and Prandtl numbers,
\begin{equation}
\mathcal{R} \equiv \sqrt{\frac{\text{Pr}}{\text{Ra}}}, \qquad \mathcal{P} \equiv \frac{1}{\sqrt{\text{Pr}\,\text{Ra}}}, \qquad
\text{Ra} = \frac{g \alpha L_z^4 \grad T_0}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}.
\end{equation}
We hold Pr$ = 1$ constant throughout this work, such that $\mathcal{P} = \mathcal{R}$.

@@

In addition to comparing the thermodynamic state achieved by the SE and AE methods,
we examine the velocities found in the evolved states.
We compute PDFs in the same manner as in Fig. \ref{fig:temp_comparison}b for the
vertical velocity (Fig. \ref{fig:pdf_comparison}a), horizontal velocity (Fig. \ref{fig:pdf_comparison}b),
and the nonlinear convective flux (Fig. \ref{fig:pdf_comparison}c). We report KS statistics
of 0.00615, 0.0349, and 0.0204, respectively.  Perhaps unsurpisingly, the nonlinear
convective transport between the SE and AE methods are very similar, as is captured
in a volume-averaged sense in the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
Each distribution shows a strong peak near zero due to the velocity boundary conditions
(Eqn. (\ref{eqn:bcs})), but the distribution of flux transport elements and velocities
is nearly identical in the AE and SE solutions.

@@

A final area in which we encourage extensions of this method is in the study of systems
operating in the presence of different thermal boundary conditions.
We have studied solutions in which we employ mixed thermal boundary conditions,
as in Eqn. (\ref{eqn:bcs}). However, the AE method can be easily applied to fixed-temperature
boundary conditions, as well.  The total evolved flux (F$_{\text{bot}}$)
through the system is not known a priori, but it can be measured using the ratios in
Eqn. (\ref{eqn:bvp_ratios}).  The integrated conductive flux is a constant which
does not change with time due to the fixed temperature jump across the domain.  
Thus, the total flux through the system can be calculated as 
$F_{\text{bot}} = \mathcal{P} / \int f_{\text{cond}} dz$. While easily extensible
to fixed-temperature boundary conditions, we hesitate to use the AE method for 
fixed-flux boundary conditions.  In those systems, there are infinitely many degenerate
solutions to the final temperature profile, and the AE method could advance the
solution into an unrealistic state as a result of an arbitrary user choice on the
temperature profile's offset.

This work serves as a first step towards creating robust methods for
achieving evolved convective solutions at high Ra on short timescales.
In order to study how astrophysical systems change over meaningful
evolutionary timescales, most studies utilize one-dimensional
systems which parameterize dynamics. However, 
modern experimentalists aim to simultaneously study system evolution
in the presence of realistic convective dynamics. We now know that it is
impossible to avoid the constraints that advective dynamics place on
timestep size \cite{viallet&all2011, viallet&all2013, viallet&all2016}
in both implicit and explicit methods. As a result, new, alternativie techniques
for evolving systems forward on thermal timescales, such as the one explored
here, must be examined in depth.

>>>>

\section{Experiment}
\label{sec:experiment}
We study incompressible \RB convection under the Oberbeck-Boussinesq approximation,
such that our fluid
has a constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
of thermal expansion ($\alpha$). The density of the fluid is a constant, $\rho_0$,
except where it is $\rho = \rho_0(1  - \alpha T_1)$ on the term where
the constant gravitational acceleration, $\bm{g} = - g\hat{z}$, 
acts in the vertical momentum equation.
The equations of motion are \cite{spiegel&veronis1960}
\begin{gather}
\DivU = 0, 
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
-\frac{1}{\rho_0}\grad P - g( 1 - \alpha T_1)\hat{z} + \nu\grad^2\bm{u}, 
	\label{eqn:dim_bouss_momentum}
\\
\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \kappa\grad^2 T_1,
	\label{eqn:dim_bouss_energy}
\end{gather}
where $\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$ is the velocity, 
$T = T_0 + T_1$ are the initial and fluctuating components of temperature, 
and $P$ is the pressure.
We non-dimensionalize these equations such that the
length is in units of the layer height ($L_z$),
temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
and velocity is in units of the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$).
by these choices, one time unit is a freefall time ($L_z/v_{\text{ff}}$).
We introduce a reduced kinematic pressure,
$\varpi \equiv (P / \rho_0 + \phi + |\bm{u}|^2 / 2) / v_{\text{ff}}^2$, where the gravitational
potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$. As $P$ is a
Langrange multiplier under the Oberbeck-Boussinesq approximation, $\varpi$
can be treated straightforwardly as a linear variable. 
In non-dimensional form, Eqns. \ref{eqn:dim_bouss_momentum} \& \ref{eqn:dim_bouss_energy}
become
\begin{gather}
\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} = \bm{u}\times\bm{\omega},
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1,
	\label{eqn:bouss_energy}
\end{gather}
where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity.
The dimensionless control parameters $\mathcal{P}$ and $\mathcal{R}$ 
are set by the Rayleigh and Prandtl numbers,
\begin{equation}
\mathcal{R} \equiv \sqrt{\frac{\text{Pr}}{\text{Ra}}}, \qquad \mathcal{P} \equiv \frac{1}{\sqrt{\text{Pr}\,\text{Ra}}}, \qquad
\text{Ra} = \frac{g \alpha L_z^4 \grad T_0}{\nu\kappa} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\kappa}, \qquad \text{Pr} = \frac{\nu}{\kappa}.
\end{equation}
We hold Pr$ = 1$ constant throughout this work, such that $\mathcal{P} = \mathcal{R}$.

@@

In addition to comparing the thermodynamic state achieved by the SE and AE methods,
we examine the velocities found in the evolved states.
We compute PDFs in the same manner as in Fig. \ref{fig:temp_comparison}b for the
vertical velocity (Fig. \ref{fig:pdf_comparison}a), horizontal velocity (Fig. \ref{fig:pdf_comparison}b),
and the nonlinear convective flux (Fig. \ref{fig:pdf_comparison}c). We report KS statistics
of 0.00615, 0.0349, and 0.0263, respectively.  Perhaps unsurpisingly, the nonlinear
convective transport between the SE and AE methods are very similar, as is captured
in a volume-averaged sense in the Nu measurements of Fig. \ref{fig:parameter_space_comparison}a\&d.
Each distribution shows a strong peak near zero due to the velocity boundary conditions
(Eqn. (\ref{eqn:bcs})), but the distribution of flux transport elements and velocities
is nearly identical in the AE and SE solutions.

@@

Stellar structure + 3-2-1 D \cite{arnett&all2015, cristini&all2016}. The
latter paper focuses on mixing on the boundaries of convective regions.
